R Notebook

### 2021-08-13 Paper_Figure_code.Rmd
small upgrades

---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

@@

```{r}
library(Metrics)
library(reshape2)
library(scales)
library(ggpubr)
library(EpiDISH)

@@

# melt_GSE107011_BPRNACan_EpiDISH_modify <- melt(GSE107011_BPRNACan_EpiDISH_modify)
# melt_FACS_107 <- melt(FACS_GSE107011[, c(1,2,4,3,5,6)]/100)

@@

Thomas_quantiseq <- as.data.frame(t(column_to_rownames(Thomas_quantiseq)))

@@

Thomas_MCP_counter <- as.data.frame(t(column_to_rownames(Thomas_MCP_counter)))

>>>>

---
title: "R Notebook"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

@@

```{r}
library(Metrics)
library(reshape2)
library(scales)
library(ggpubr)
library(EpiDISH)
library(tidyverse)
library(immunedeconv)

@@

melt_GSE107011_BPRNACan_EpiDISH_modify <- melt(GSE107011_BPRNACan_EpiDISH_modify)
melt_FACS_107 <- melt(FACS_GSE107011[, c(1,2,4,3,5,6)]/100)

@@

Thomas_quantiseq <- as.data.frame(t(column_to_rownames(Thomas_quantiseq, var = "cell_type")))

@@

Thomas_MCP_counter <- as.data.frame(t(column_to_rownames(Thomas_MCP_counter, var = "cell_type")))
